Evaluating the Importance of Initial Conditions for Antarctic Sea Ice Seasonal Predictability with a Fully Coupled Forecast Model

### 2025-10-30 analysis/paper/access-ice.qmd
Fixes caption

```{r fig-bias-1}
#| fig-cap: !expr glue::glue("Ensemble mean difference between monthly sea-ice concentration of +S2 ensemble mean forecast at 0-month lead time (monthly mean values forecasted from the forecast initialised at the first of the month) and observations ({labs_dataset[which_dataset]})").
#| fig-height: 6

>>>>

```{r fig-bias-1}
#| fig-cap: !expr glue::glue("Ensemble mean difference between monthly sea-ice concentration of +S2 ensemble mean forecast at 0-month lead time (monthly mean values forecasted from the forecast initialised at the first of the month) and observations ({labs_dataset[which_dataset]}).")
#| fig-height: 6
